---
title: "Colors"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Colors}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, message = FALSE}
library(omni)
library(tidyverse)
```

The package provides color and fill scales to match the OMNI color palette. Here is the "Main" color palette.

> There is a `omni_colors()` function that allows you to extract individual colors. You can choose from: Gray, Dark Blue, Medium Blue, Light Blue, Teal, Orange, and Tan.

```{r echo = FALSE}
scales::show_col(omni_colors())
```

You can add the line `scale_fill_omni_discrete()` to change the fill on a plot.

```{r}
iris |>
  group_by(Species) |>
  summarise(sepal_length_mean = mean(Sepal.Length)) |>
  ggplot(ggplot2::aes(x = Species, y = sepal_length_mean, fill = Species)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  scale_fill_omni_discrete() +
  theme_omni(show_legend = FALSE)
```

You can change the palette by using the palette argument.

```{r}
iris |>
  group_by(Species) |>
  summarise(sepal_length_mean = mean(Sepal.Length)) |>
  ggplot(ggplot2::aes(x = Species, y = sepal_length_mean, fill = Species)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  scale_fill_omni_discrete(palette = "Blues") +
  theme_omni(show_legend = FALSE)
```

You can reverse the order by using the reverse argument.

```{r}
iris |>
  group_by(Species) |>
  summarise(sepal_length_mean = mean(Sepal.Length)) |>
  ggplot(ggplot2::aes(x = Species, y = sepal_length_mean, fill = Species)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  scale_fill_omni_discrete(palette = "Blues",
                           reverse = TRUE) +
  theme_omni(show_legend = FALSE)
```

There is also a `scale_fill_omni_continuous()` function as well as `scale_color_omni_discrete()` and `scale_color_omni_continuous()` functions for colors.

You can specify a list of colors if needed :

```{r}
iris |>
  group_by(Species) |>
  summarise(sepal_length_mean = mean(Sepal.Length)) |>
  ggplot(ggplot2::aes(x = Species, y = sepal_length_mean, fill = Species)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  scale_fill_omni_discrete(palette = c("Dark Blue", "Orange", "Tan")) +
  theme_omni(show_legend = FALSE)
```


