---
title: "Colors"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Colors}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(omni)
```

The package provides color and fill scales to match the OMNI color palette. Here is the "Main" color palette.

```{r echo = FALSE}
scales::show_col(omni_palettes$Main)
```

And here is the "Blues" palette (i.e. it just uses the blue colors in the OMNI palette).

```{r echo = FALSE}
scales::show_col(omni_palettes$Blues)
```

You can add the line `scale_fill_omni_discrete()` to change the fill on a plot.

```{r}
iris %>%
  dplyr::group_by(Species) %>%
  dplyr::summarise(sepal_length_mean = mean(Sepal.Length)) %>%
  ggplot2::ggplot(ggplot2::aes(x = Species, y = sepal_length_mean, fill = Species)) +
  ggplot2::geom_bar(stat = "identity") +
  ggplot2::coord_flip() +
  scale_fill_omni_discrete() +
  theme_omni(show_legend = FALSE)
```

You can change the palette by using the palette argument.

```{r}
iris %>%
  dplyr::group_by(Species) %>%
  dplyr::summarise(sepal_length_mean = mean(Sepal.Length)) %>%
  ggplot2::ggplot(ggplot2::aes(x = Species, y = sepal_length_mean, fill = Species)) +
  ggplot2::geom_bar(stat = "identity") +
  ggplot2::coord_flip() +
  scale_fill_omni_discrete(palette = "Blues") +
  theme_omni(show_legend = FALSE)
```

You can reverse the order by using the reverse argument.

```{r}
iris %>%
  dplyr::group_by(Species) %>%
  dplyr::summarise(sepal_length_mean = mean(Sepal.Length)) %>%
  ggplot2::ggplot(ggplot2::aes(x = Species, y = sepal_length_mean, fill = Species)) +
  ggplot2::geom_bar(stat = "identity") +
  ggplot2::coord_flip() +
  scale_fill_omni_discrete(palette = "Blues",
                           reverse = TRUE) +
  theme_omni(show_legend = FALSE)
```

There is also a `scale_fill_omni_continuous()` function as well as `scale_color_omni_discrete()` and `scale_color_omni_continuous()` functions for colors.

Need more control? There is a `omni_colors()` function that allows you to extract individual colors. You can choose from: Dark Gray, Dark Blue, Medium, Blue, Light Blue, Teal, Orange, and Tan.

```{r}
iris %>%
  dplyr::group_by(Species) %>%
  dplyr::summarise(sepal_length_mean = mean(Sepal.Length)) %>%
  ggplot2::ggplot(ggplot2::aes(x = Species, y = sepal_length_mean, fill = Species)) +
  ggplot2::geom_bar(stat = "identity") +
  ggplot2::coord_flip() +
  ggplot2::scale_fill_manual(values = c(omni_colors("Dark Blue", "Orange", "Tan"))) +
  theme_omni(show_legend = FALSE)
```

