---
title: "Colors"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Colors}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
    warning = FALSE,
    message = FALSE,
    collapse = TRUE,
    comment = "#>"
)
```

```{r setup, message = FALSE}
library(omni)
library(tidyverse)
```

The package provides color and fill scales to match the OMNI color palette. Here is the "Main" color palette.

> There is a `omni_colors()` function that allows you to extract individual colors. You can choose from: "white", "ivory", "ivory 400", "orange-red 200", "orange-red 400", "orange-red 600", "golden-yellow 200", "golden-yellow 400", "golden-yellow 600", "olive-green 200", "olive-green 400", "olive-green 600", "teal 200", "teal 400", "teal 600", "plum 200", "plum 400", "plum 600", "periwinkle 200", "periwinkle 400", "periwinkle 600", "steel blue 200", "steel blue"

```{r echo = FALSE}
scales::show_col(omni_colors())
```

You can add the line `scale_fill_omni_discrete()` to change the fill on a plot.

```{r}
iris |>
    group_by(Species) |>
    summarise(sepal_length_mean = mean(Sepal.Length)) |>
    ggplot(ggplot2::aes(x = Species, y = sepal_length_mean, fill = Species)) +
    geom_bar(stat = "identity") +
    coord_flip() +
    scale_fill_omni_discrete() +
    theme_omni(show_legend = FALSE)
```

You can change the palette by using the palette argument.

```{r}
iris |>
    group_by(Species) |>
    summarise(sepal_length_mean = mean(Sepal.Length)) |>
    ggplot(ggplot2::aes(x = Species, y = sepal_length_mean, fill = Species)) +
    geom_bar(stat = "identity") +
    coord_flip() +
    scale_fill_omni_discrete(palette = "teal") +
    theme_omni(show_legend = FALSE)
```

You can reverse the order by using the reverse argument.

```{r}
iris |>
    group_by(Species) |>
    summarise(sepal_length_mean = mean(Sepal.Length)) |>
    ggplot(ggplot2::aes(x = Species, y = sepal_length_mean, fill = Species)) +
    geom_bar(stat = "identity") +
    coord_flip() +
    scale_fill_omni_discrete(palette = "teal", reverse = TRUE) +
    theme_omni(show_legend = FALSE)
```

There is also a `scale_fill_omni_continuous()` function as well as `scale_color_omni_discrete()` and `scale_color_omni_continuous()` functions for colors.

You can specify a list of colors if needed :

```{r}
iris |>
    group_by(Species) |>
    summarise(sepal_length_mean = mean(Sepal.Length)) |>
    ggplot(ggplot2::aes(x = Species, y = sepal_length_mean, fill = Species)) +
    geom_bar(stat = "identity") +
    coord_flip() +
    scale_fill_omni_discrete(
        palette = c("olive-green 200", "golden-yellow 400", "orange-red 600")
    ) +
    theme_omni(show_legend = FALSE)
```


