---
title: "Theme"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Theme}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  comment = "#>"
)
```

```{r setup}
library(omni)
```

You can add the function `omni_theme()` to the end of any ggplot2 pipeline and it will generate plots that look like the same. The theme uses minimalist gridlines and the Lato font throughout. 

```{r}
iris %>%
  dplyr::group_by(Species) %>%
  dplyr::summarise(sepal_length_mean = mean(Sepal.Length)) %>%
  ggplot2::ggplot(ggplot2::aes(x = Species, y = sepal_length_mean, fill = Species)) +
  ggplot2::geom_bar(stat = "identity") +
  ggplot2::coord_flip() +
  scale_fill_omni_discrete() +
  theme_omni()
```


The `theme_omni()` function has two arguments. `show_grid_lines` (set to TRUE by default) determines whether or not grid lines show up. Here's a plot with no grid lines.

```{r}
iris %>%
  dplyr::group_by(Species) %>%
  dplyr::summarise(sepal_length_mean = mean(Sepal.Length)) %>%
  ggplot2::ggplot(ggplot2::aes(x = Species, y = sepal_length_mean, fill = Species)) +
  ggplot2::geom_bar(stat = "identity") +
  ggplot2::coord_flip() +
  scale_fill_omni_discrete() +
  theme_omni(show_grid_lines = FALSE)
```

The second argument is `show_legend` (set to TRUE by default). Here's a plot with the legend removed.

```{r}
iris %>%
  dplyr::group_by(Species) %>%
  dplyr::summarise(sepal_length_mean = mean(Sepal.Length)) %>%
  ggplot2::ggplot(ggplot2::aes(x = Species, y = sepal_length_mean, fill = Species)) +
  ggplot2::geom_bar(stat = "identity") +
  ggplot2::coord_flip() +
  scale_fill_omni_discrete() +
  theme_omni(show_legend = FALSE)
```
