---
title: "Project Name: Cleaning and Analysis"
author: "Your Name"
date: "`r format(Sys.Date(), '%d %B, %Y')`"
output: 
  html_document:
    toc: true
    toc_depth: 4
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## File Description

Write a couple sentences here about what this Markdown file does. It can be as detailed as you would like, but should be detailed enough that other project staff will be able to open it and know what is going on. 

**Example** This file is the template R Markdown file for data cleaning and analysis at the OMNI Institute. It was created on 1/30/20 by Elaine Maskus, and updated on 5/6/20. In it you will find best practices for loading packages and data, documenting various processes, and more! Our goal in the future is to have OMNI formatting built in (i.e. colors, fonts, etc.). Happy coding!

**Saving your Markdown File**
When saving your file, make sure not to include any spaces or special characters in the file name. Markdown will convert these or have trouble reading them, which can cause you to have multiple versions. Also, when typing the file name _make sure to type .Rmd at the end of your file name_ to save it as an R Markdown document.

```{r packages, message = FALSE, warning=FALSE}
# this code chunk should load all of the packages you will be using in the file.
library(tidyverse) #loads multiple packages for BP data management, viz, and more. Should always include
library(openxlsx) #for reading and writing excel files
library(janitor) #for cleaning data
library(summarytools) #for easily summarizing data
# above are some standard packages that are used across the organization. Add or delete any additional packages as needed. Remember, a package only needs to be installed once per computer then you can use it in all scripts using the library() function.
# to install a package for the first time use install.packages("package_name")
```

## Loading Data

Write a description of the data files here if you want to.

```{r data, echo=TRUE, eval = TRUE}
# .csv data
df_name <- read_csv("pathway/file_name.csv", na = c("-99","NA")) %>% 
    clean_names() 
# excel data
df_name <- read.xlsx("pathway/file_name.xlsx", na = "--") %>%
  clean_names()
# label NA's in your .csv using na = ""
# clean_names() is part of the janitor package, it creates unified and clean naming structure for all variables
# see the R Trello board for loading differnt data file types (SPSS, tab delimited, etc.)
```

## Cleaning Step 1

Description of what below code is doing (i.e. Re-naming variables, re-coding values)

```{r, echo = T}
## your code here
```

## Cleaning Step 2 / Analysis / Next Part of Your Syntax

Description of what below code is doing.

```{r, echo = T}
## your code here
```
