---
title: "test"
output: html_document
---

<script>
  document.addEventListener("DOMContentLoaded", () => {
    const shadowHosts = document.querySelectorAll(
    '.flextable-shadow-host'
    );
  
    if (shadowHosts) {
      shadowHosts.forEach(shadowHost => {
        const shadowRoot = shadowHost.shadowRoot;
        if (shadowRoot) {
          const caption = shadowRoot.querySelector('div.tabwid caption');
          if (caption) {
            caption.style.textAlign = 'left';
            caption.style.color = "#677384"
            caption.style.fontSize = "11pt";
            caption.style.fontFamily = "Inter Tight";
          }
        } else {
        console.warn("Shadow host .flextable-shadow-host not found.");
        }
      })
    }
  });

</script>



# One Table

```{r}
#| tbl-cap: "Table 1. [Insert Table Name]"
palmerpenguins::penguins |> 
  dplyr::slice(1:3) |>
  dplyr::mutate(year = as.character(year)) |>
  omni::omni_table(caption = 'Table 1. [Insert Table Name]')
```

# One more without caption

```{r}
palmerpenguins::penguins |> 
  dplyr::slice(1:3) |>
  dplyr::mutate(year = as.character(year)) |>
  omni::omni_table(caption = 'Table 1. [Insert Table Name]')
```

# One more with caption again

```{r}
#| tbl-cap: "Table 1. [Insert Table Name]"
palmerpenguins::penguins |> 
  dplyr::slice(1:3) |>
  dplyr::mutate(year = as.character(year)) |>
  omni::omni_table(caption = 'Table 1. [Insert Table Name]')
```

